---
title: "Variables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
```



```{r}
diversity <- read.csv(file = "../data-raw/Dryad_Data.csv")
head(diversity)
```

```{r}
butterfly_diversity <- diversity$Butterfly.Diversity 
floral_diversity <- diversity$Floral.Diversity
butterfly_richness <- diversity$Butterfly.Richness
head(butterfly_diversity)
str(butterfly_diversity)
```



```{r}
cor(diversity$Butterfly.Diversity, diversity$Floral.Diversity) #Positive Correlation
```

```{r}
library(ggplot2)

ggplot(data = diversity, mapping = aes(x = butterfly_diversity, y = floral_diversity)) +
geom_point(size = 3, color = "blue", alpha = 0.5) +
scale_y_log10() +
scale_x_log10()
```

### Floral diversity has a positive effect on butterfly diversity. Positive correlation is the positive relationship between two variables as the movement of the variables' is positively linked.



```{r}
cor(diversity$Butterfly.Diversity, diversity$Grasshopper.Attacks) # Low Correlation

```

```{r}
ggplot(data = diversity, mapping = aes(x = butterfly_diversity, y = Grasshopper.Attacks)) +
geom_point(size = 3, color = "blue", alpha = 0.5) +
scale_y_log10() +
scale_x_log10()
```

### As we have seen before, the correlation coefficient is at 0.31 falling in the range of having low correlation therefore contributing to a lack of a linear relationship. There is little to none correlation between the Butterfly Diversity and Grasshopper Attacks. 

```{r}
cor(diversity$Site.Area, diversity$Floral.Diversity) #positive correlation
```

```{r}
ggplot(data = diversity, mapping = aes(x = Site.Area, y = Floral.Diversity)) +
geom_point(size = 3, color = "red", alpha = 0.5) +
scale_y_log10() +
scale_x_log10()
```

### The correlation coefficient falls at 0.58 depicting a positive correlation that there is a relationship between the site area increasing floral diversity.


```{r}
cor(diversity$Site.Area, diversity$Predator.Attacks) #Positive Correlation

```

```{r}
ggplot(data = diversity, mapping = aes(x = Site.Area, y = Predator.Attacks)) +
geom_point(size = 3, color = "blue", alpha = 0.5) +
scale_y_log10() +
scale_x_log10()
```
```{r}
ggplot(data = diversity, mapping = aes(x = Site.Area, y = Predator.Attacks), color = "gray", alpha = 0.5) +
  geom_point(color = "gray") +
  geom_point(data = diversity, mapping = aes(x = Site.Area, y = Predator.Attacks), color = "red", alpha = 0.6) +
  geom_smooth() +
geom_smooth(data = diversity, mapping = aes(x = Site.Area, y = Predator.Attacks))
```

### The Site Area and Predator Attacks are strongly correlated with a correlation coefficient of 0.96 which indicates there is a strong linear relationship between the two. This implies that the predation occurs in more larger and isolated sites wherease predators correspond to more landscape characteristics rather than the butterfly community.

